{\ttlit Bug Seeding}, On the importance of Previous Commit

### 2016-01-25 paperMSR.tex
adding text

\section{Introduction}
\label{sec:introduction}
In order to investigate if this assumption is valid, we formulate following research questions:
\begin{itemize}
    \item RQ1 : How can tickets which are bug reports be differentiated from those that are not? 
    \item RQ2:  How often is the bug caused in the previous commit? 
\end{itemize}

%The remainder of this paper is structured as follows; first, we discuss how to extract and classify data from specific repository of OpenStack in Section~\ref{}. In this repository we can find tickets that describe bugs; however, in order to obtain a successful results, we need know how many of them are bug reports. This problem is solved in Subsection~\ref{}, answering in this way RQ1. After having discriminated bug reports from those that are not, to answer the RQ2 we have calculated how many times the cause of the bug could be attributed to the previous commit (see Subsection~\ref{subsec:second}). Results are then shown in Section~\ref{}. Finally, we present a discussion, including the threats to validity, in Section~\ref{}.

\section{The Case of Study}
\label{sec:caseStudy}
\subsection{Fist Stage: The Filtering}
\label{sec:firstStage}
%OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, furthermore due to its short life, only 5 years, all history is saved and available in a version control system. The issues are called tickets in OpenStack and available in the Launchpad, a web interface of ticket tracking system, classifying them as bug report or not.

@@

\subsubsection{The Tool}
\label{sec:tool}
%A tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not. The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports, making the process easier, faster, and more reliable.

@@

At this stage, we got a list with all the previous commits, which could be where the bug was introduced. We have to identify those previous commits responsible for inserting the line with the bug. When there are more than one commit implicated in the same file is because the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, after the analysis the responsible can be only one of them or maybe two, in fact sometimes all of them were responsible. Therefore, comparing the status of the file, before and after the commit, we are be able to identify those previous commits that are responsible and those that are not, answering the RQ2.

@@

\subsection{Fist Stage}
\label{sec:resultsFS}
%We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron. The table \ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers, 
\begin{table*}
\centering
%\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{lllll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
Developer 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
Developer 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
Developer 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
\bottomrule[0.3mm]
\end{tabular} %}
%\end{center}
\end{table*}

@@

%\begin{table}[htb]
%\begin{center} {\footnotesize
%\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
%\label{secondStage}
%\begin{tabular}{lcc}
%\toprule[0.3mm]
%  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
%  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
%\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
%\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
%\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
%\bottomrule[0.3mm]
%\end{tabular} }
%\end{center}
%\end{table}

\section{Discussion}
\label{sec:discussion}
%This section presents first the threats to the validity of our study. Then, it discusses the possible applications and introduces the work that still has to be done.

@@

%In the preliminary results we have observed that the current premise, based on the SZZ algorithm, does not hold in all cases. Around half of the previous commits analyzed have been identified as responsible for inserting the line with the bug. Thus, the articles based on SZZ algorithm may be based on a wrong assumption. However, a larger number of tickets has to be studied to ascertain that our findings can be generalized. Our idea is contribute with this study in the knowledge about the responsibility practiced by the previous commit in a bug, helping to the software engineering community in the code review process. FIXME: aclarar esta frase que no me queda clara: Our idea is propose a reinterpretation in the responsibility practiced by the previous commit in a bug.

%In the next months, we will carry out another empirical study with a larger sample size to prove that our results can be generalized. In this way, with a larger population we may be able to find certain patterns that we are now omitting. Furthermore, we extend this study to other projects to ascertain that what we have found occurs regardless of the project analyzed, because the OpenStack may be a special project, where the code is evolving continuously. In fact, we can access a huge database of other projects such as Eclipse or Mozilla that will allow us analyze this assumption, and where we will use statistical analysis to compare the results obtained in the different projects.

%In addition, we have developed a tool that automatizes the first stage, displaying all the information used in the analysis in a web page\footnote{\url{http://bugtracking.libresoft.es}}, decreasing the time used in the analysis for the first stage. The future work with the tool will focus on improving and automating the second stage.

>>>>

\section{Introduction}
\label{sec:introduction}
How to plan to apply the knowledge in a way that can benefit software engineers.
What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?

In order to investigate if this assumption is valid, we formulate following research questions:
\begin{itemize}
    \item RQ1 : How can tickets which are bug reports be differentiated from those that are not? 
    \item RQ2:  How often is the bug caused in the previous commit? 
\end{itemize}

The remainder of this paper is structured as follows; first, we discuss how to extract and classify data from specific repository of OpenStack in Section~\ref{}. In this repository we can find tickets that describe bugs; however, in order to obtain a successful results, we need know how many of them are bug reports. This problem is solved in Subsection~\ref{}, answering in this way RQ1. After having discriminated bug reports from those that are not, to answer the RQ2 we have calculated how many times the cause of the bug could be attributed to the previous commit (see Subsection~\ref{subsec:second}). Results are then shown in Section~\ref{}. Finally, we present a discussion, including the threats to validity, in Section~\ref{}.

\section{The Case of Study}
\label{sec:caseStudy}
\subsection{Fist Stage: The Filtering}
\label{sec:firstStage}
OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, furthermore due to its short life, only 5 years, all history is saved and available in a version control system. The issues are called tickets in OpenStack and available in the Launchpad, a web interface of ticket tracking system, classifying them as bug report or not.

@@

\subsubsection{The Tool}
\label{sec:tool}
A tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not. The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports, making the process easier, faster, and more reliable.

@@

At this stage, we got a list with all the previous commits, which could be where the bug was introduced. We have to identify those previous commits responsible for inserting the line with the bug. When there are more than one commit implicated in the same file is because the bug was inserted in different lines of different commits, but not everyone has to be responsible for the commit, after the analysis the responsible can be only one of them or maybe two, in fact sometimes all of them were responsible. Therefore, comparing the status of the file, before and after the commit, we are be able to identify those previous commits that are responsible and those that are not, answering the RQ2.
\subsubsection{Discarting False Positives}
\label{sec:discarting}
We have to discart these previous commits that change the format, that add blank spaces and that change comments.
¿What happen with the lines which are copied from others previous commits?

@@

\subsection{Fist Stage}
\label{sec:resultsFS}
We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron. The table \ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers, 
\begin{table*}
\centering
%\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{lllll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
Developer 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
Developer 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
Developer 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
\bottomrule[0.3mm]
\end{tabular} %}
%\end{center}
\end{table*}

@@

\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
\label{secondStage}
\begin{tabular}{lcc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

After discarding the noise caused by the false positives the results are:
\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Probability of cause the bug depending on how many previous commits had the bug report}
\label{secondStage}
\begin{tabular}{lcc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous } & \multicolumn{1}{c}{More than one previous} \\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commit} \\\hline
\raisebox{1ex}{Responsible} & 75.86\% & 46.32\% \\[0ex]
\raisebox{1ex}{Not responsible} & 6.9\% & 44.21\%\\[0ex]
\raisebox{1ex}{Undecided} & 17.24\% & 9.47\%\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

\section{Discussion}
\label{sec:discussion}
This section presents first the threats to the validity of our study. Then, it discusses the possible applications and introduces the work that still has to be done.

How to proceed if looking for the responsability of a bug when only added lines are inserted? And we are talking about a bug report not a new feature, these kinds of cases use to be when a developer forgot check some case inside a function. [reference]
\begin{enumerate}
\item Is responsible the function where these lines are content?
\item Is responsible the last commit that modify something in the function?
\end{enumerate}

@@

In the preliminary results we have observed that the current premise, based on the SZZ algorithm, does not hold in all cases. Around half of the previous commits analyzed have been identified as responsible for inserting the line with the bug. Thus, the articles based on SZZ algorithm may be based on a wrong assumption. However, a larger number of tickets has to be studied to ascertain that our findings can be generalized. Our idea is contribute with this study in the knowledge about the responsibility practiced by the previous commit in a bug, helping to the software engineering community in the code review process. FIXME: aclarar esta frase que no me queda clara: Our idea is propose a reinterpretation in the responsibility practiced by the previous commit in a bug.

In the next months, we will carry out another empirical study with a larger sample size to prove that our results can be generalized. In this way, with a larger population we may be able to find certain patterns that we are now omitting. Furthermore, we extend this study to other projects to ascertain that what we have found occurs regardless of the project analyzed, because the OpenStack may be a special project, where the code is evolving continuously. In fact, we can access a huge database of other projects such as Eclipse or Mozilla that will allow us analyze this assumption, and where we will use statistical analysis to compare the results obtained in the different projects.

In addition, we have developed a tool that automatizes the first stage, displaying all the information used in the analysis in a web page\footnote{\url{http://bugtracking.libresoft.es}}, decreasing the time used in the analysis for the first stage. The future work with the tool will focus on improving and automating the second stage.
